Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-31 journal/article.tex
T: Communities: Work in progress

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Change leaders         &  Described in  \\
        \midrule
        High-up change leaders or sponsors  &
                P3, P5, P24, P31, P36, P38, P46, P49  \\
        Agile task group for coordinating change   &
                P4, P16, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        Change leaders on other organizational levels  &
                P2, P6, P9, P14, P17, P18, P27  \\
        Informal spreading of agile awareness  &
                P3, P6, P40  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of entities leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

Change leadership showed on the lowest level as informal spreading of awareness
of agile methods.
Benefield [P6] describes that the strongest force over other change leaders was
letting agile knowledge spread virally. New Scrum teams were emerging as people
heard of the new methodology [P6].
It was similarly described that in an organization with an introverted culture
the proclamations of managers could not match with the power of practitioners
explaining to others how they had succeeded in with the agile method [P40].
Even casual hallway talks could spread the word effectively, and it was
also easier to encounter people from other parts of the organization in an
informal context [P3].

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
        In-house coaching   &
                P1-P3, P6, P11, P16, P23, P29, P31, P32,
                P39, P41, P45, P47, P49, P50, P52  \\    % 17
        Seminars and workshops   &
                P1-P4, P7, P9, P10, P11, P16, P23, P25,
                P26, P27, P32, P41, P44, P46, P47   \\   % 18
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

% Content of events
In addition to general training and enabling awareness, the purpose of agile
events was to evangelize and expand the agile model throughout the organization
[P1, P10, P23, P32, P46].
Workshops were used to get people better involved [P16], and public lectures
were used to set straight sidetracks in the agile implementation[P26].
Hands-on workshops were used as a more engaging teaching method compared to
traditional lectures [P32, P41]. Open events were good for delivering the same
message to many people at the same time. As everyone could heard the same
questions and answers the understanding was consistent [P9, P41].
Workshops were arranged for identifying problems and planning the new model [P7,
P16, P27].

@@

>>>>

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Change leaders         &  Described in  \\
        \midrule
        High-up change leaders or sponsors  &
                P3, P5, P24, P31, P36, P38, P46, P49  \\
        Agile task group for coordinating change   &
                P4, P16, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        Change leaders on other organizational levels  &
                P2, P6, P9, P14, P17, P18, P27  \\
        Informal spreading of agile awareness  &
                P3, P6, P14, P40  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of entities leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

Change leadership showed on the lowest level as informal spreading of awareness
of agile methods.
Benefield [P6] describes that the strongest force over other change leaders was
letting agile knowledge spread virally. New Scrum teams were emerging as people
heard of the new methodology [P6]. In some cases interest groups were used to
stimulate viral spreading of agile [P14].
It was similarly described that in an organization with an introverted culture
the proclamations of managers could not match with the power of practitioners
explaining to others how they had succeeded in with the agile method [P40].
Even casual hallway talks could spread the word effectively, and it was also
easier to encounter people from other parts of the organization in an informal
context [P3].

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
        In-house coaching   &
                P1-P3, P6, P11, P16, P23, P29, P31, P32,
                P39, P41, P45, P47, P49, P50, P52  \\    % 17
        Seminars and workshops   &
                P1-P4, P7, P9, P10, P18, P11, P16, P23, P25,
                P26, P27, P32, P41, P44, P46, P47   \\   % 18
        Communities, special interest groups  &
                P3, P6, P7, P9, P10, P11, P12, P14, P32, P41,
                P42, P45, P47, P52  \\   % 14 
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

% Content of events
In addition to general training and enabling awareness, the purpose of agile
events was to evangelize and expand the agile model throughout the organization
[P1, P10, P23, P32, P46].
Workshops were used to get people better involved [P16], and public lectures
were used to set straight sidetracks in the agile implementation [P26].
Hands-on workshops were used as a more engaging teaching method compared to
traditional lectures [P32, P41]. Open events were good for delivering the same
message to many people at the same time. As everyone could heard the same
questions and answers the understanding was consistent [P9, P41].
Workshops were arranged for identifying problems and planning the new model [P7,
P16, P27].

% SIGs, CoPs, and community

What?

Why?

For whom?

Benefit?

Events and coaching activity were coordinated forms of promoting the new model,
but the agile transformation gave also birth to communities [P3]. Typically
communities were emerging later in the transformation, when the rollout team
was starting to step aside [P3, P41].
In some cases the communities were created by passionate individuals without
corporate intervention, and participation in communities was voluntary [P47].
Communities were created when the mass of people involved became too large for
formal control [P52].
In other cases the forming of communities was stimulated by the organization
[P12, P45].
Companies strived to create communities of practice [P42] or special interest
groups [P41] in order to reinforce continuous learning in the organization.
Communities helped people to form a learning habit, which promoted continuous
improvement in the organization [P52].

@@

[P3]
* Who: Employees
* When: During transformation
* When: The community stayed
* What: There were e-mail lists
* What: Discssion forums were used for direct conversation instead of using the change leader
* Particular: It is claimed that communities are often used
* Benefit: Reinforcing agile practices

[P6]
* Who: People
* What: Mailing list for sharing information on agile
* What: Pockets of committed communities
* Purpose: Leveraging promoting force of people in the trenches

[P7]
* Who: Scrum masters
* When: Beginning
* What: Peer groups for Scrum masters
* Benefit: The peer groups evolved into a Scrum master community
* Benefit: The community was essential in growing managers to agile roles

[P9]
* When: In the transformation
* What: People attended to external communities, there were internal champions
* Benefit: The movement created interest in agile

[P10]
* Who: tems
* What: Teams started communicating through e-mail groups
* What: Use of wikis, informal gatherings
* Particular: The interest was voluntary, the company started creating official programme

[P11]
* Who: Scrum masters, people managers
* What: Scrum masters met regularly --> Helped coordinate work
* Particular: Product owners should also have formed their own community

[P12]
* Who: Everyone
* Why: The organization introduced a matrix structure
* What: People met peers from other parts of the company, there were discipline specific meetings
* Benefit: People started talking with each other
* Particular: The agile culture was initiated

[P14]
* What: Agile support group
* What: Attempted to support viral spreading of agile

[P32]
* What: A coaching community
* Particular: The community took time to build, as coaching is a skill not learned easily

[P41]
* When: The transition team moved aside
* Who: Scrum master, teams
* What: Special interest groups were formed to reinforce the new practices
* Purpose: Create learning organization

[P42]
* Why: Needed for creating a learning organization and evolve the organization
* What: Communities of practice
* What: Bring in as many ideas as possible
* Purpose: Create learning organization

[P45]
* What: All data from teams was gathered
* Purpose: Set up a network of information for Scrum masters and product owners
* Purpose: Create a round table of experts

[P47]
* When: Broader adoption of agile
* Why: Coaches saw a need to create an environment to support learning and influence agile
* What: Coach community, supported by a particular experienced team
* Particular: voluntarily participation
* Particular: It was created by passionate individuals rather than management decision
* What: The community organizes agile events

[P52]
* When: There was many scrum masters
* What: Community of Scrum masters
* Why: The team of Scrum masters became so big that it was hard to coordinate formally.
       They started changing experiences less formally, in order to become better in the task.
* Benefit: When people started contributing from the wider scope a positive feedback loop was created
* Benefit: People developed a learning habit, continuous improvement in the organization
